\vspace{-2cm}A generative model for urban firm networks

### 2021-01-05 Response_to_reviewers.tex

% recipient data
\recipient{Editor PONE}{}
\date{\today}
\opening{Dear Editor,}
\closing{Yours faithfully,\\
Juste Raimbault and co-authors\\
University College London
}
         % use an optional argument to use a string other than "Enclosure", or redefine \enclname

%\makelettertitle

\justify

\textbf{Action points}

\begin{itemize}
    \item[All]
    \begin{itemize}
        \item Rewrite literature review
        \item discuss possible extension with self-connex
        \item better model description
        \item paper positioning
        \item paper writing (ex jargon, clarity)
    \end{itemize}
    \item[JR]
    \begin{itemize}
        \item Discuss choice/possibly test other stat models - Hurdle, etc.
        \item total time is linked to $w_0$ - discuss this
        \item this is not a prediction model - possibly give values of abs error - discuss more model function
        \item compute more empirical indicators and compare  with generated networks
        \item technical clarifications
    \end{itemize}
    \item[NZ]
    \begin{itemize}
        \item geo lit choice indics
        \item more precise data description
    \end{itemize}
\end{itemize}

@@

	\medskip

%1.2 -

	\item \textit{The empirical network is sparse (density ~ 0.03). Do the authors consider the absent links in the regression and/or the generative model they propose ? (from the fact that the log is taken in the statistical model and the computation of the mean square error on logs, it appears that it is not the case). This could be made clear and discussed, especially that the absence of links is the norm rather than the exception, meaning that the model only treats only a minor proportion of cases.}

	$\rightarrow$ \todo{(JR) Discuss choice/possibly test other stat models}

@@

	\medskip

%1.3 -

	\item \textit{Given that the model is generative, the temporal aspect of the model can be an issue. Indeed, if the number of iterations (around 5000) needed to generate the empirical network correspond to a long time period (for example decades), the economic size and sectoral proximity are expected to change, probably implying a substantially different network, if these changes were accounted for in the model. Can the authors mention (and may be discuss) this issue?}

	$\rightarrow$ \todo{(JR) total time is linked to $w_0$ - discuss this}

@@

	\medskip

%1.4 -

	\item \textit{Application: Two potentially problematic aspects: 1) the MSE on logs and the log MSE appear to be quite large to perform an accurate prediction (for an MSE on logs $\sim 5$, the average multiplicative error can roughly be expected to be around $\exp(5^0.5) \sim 9$, which is almost an order of magnitude of difference; the same quick calculation can be applied to the log MSE). Can the authors discuss this point? (May be using a mean absolute error instead of mean squared error is a more tangible estimate of the error?)}

	$\rightarrow$ \todo{(JR) this is not a prediction model - possibly give values of abs error - discuss more model function}

@@

	\medskip

	\item \textit{2) The authors do not show how well the model reproduces the metropolization and the communities of the empirical network. If the model does not perform well at reproducing these properties of the network, it can mean that the predictors they used are not relevant to such features. This would imply that the model is of limited relevancy to study the impact of crises on these structural features.}

	$\rightarrow$ \todo{(JR) compute more empirical indicators and compare  with generated networks}

@@

	\medskip

%### Minor issues
%2.1 -

	\item \textit{Do you consider self-connections in the network ? These have been shown to represent an important proportion of firm ownership links.}

	$\rightarrow$ \todo{(All) discuss possible extension with self-connex}

@@

	$\rightarrow$ \todo{(All) paper positioning}

	\medskip

%2.
	\item \textit{Clarify the jargon. What is a 'generative model'? What is 'synthetic' data?}

	$\rightarrow$ \todo{(All) paper writing (ex jargon, clarity)}

### 2021-02-23 Response_to_reviewers.tex

% recipient data
\recipient{Editor PONE}{}
\date{\today}
\opening{Dear Editor,}
\closing{Yours faithfully,\\
Juste Raimbault and co-authors\\
University College London
}
         % use an optional argument to use a string other than "Enclosure", or redefine \enclname

%\makelettertitle

\justify

\textbf{Action points}

\begin{itemize}
    \item[All]
    \begin{itemize}
        \item Paper writing (jargon, clarity, nonsense in Fig 4 legend on gravity (?))
        \item Improve model description
        \item Rewrite literature review, theoretical framing, more literature on included processes
        \item Paper positioning: rewrite
        \item Discuss possible extension with self-connection e.g.
        \item Justify application to economic shocks is a proof-of-concept - add literature
    \end{itemize}
    \item[JR]
    \begin{itemize}
        \item Discuss choices of stat models (link with literature); possibly test other stat models - Hurdle, Gamma etc. (discuss missing data treated differently than actual zeros)
        \item This is not a prediction model: discuss more model function; possibly give values of abs error
        \item Compute more indicators on empirical data and compare with generated networks (the comparison is only on fitting indicators for now)
        \item Technical clarifications (total time is linked to $w_0$; over-fitting)
    \end{itemize}
    \item[NZ]
    \begin{itemize}
        \item More geographical literature for the choice of indicators, theoretical framing of processes
        \item More precise data description, descriptive statistics
    \end{itemize}
\end{itemize}

@@

%### Major issues

\begin{enumerate}
%1.1 -

	\item \textit{The work is at the intersection of three strands of literature: a) spatial interaction models, b) network analysis, and c) preferential attachment. Yet this does not appear in the literature review. The work could gain more depth from a better discussion of the literature it is grounded in.}

	$\rightarrow$ \todo{(All) Rewrite lit review. Include applications of gravity models to trade and migration.}

@@

	$\rightarrow$ \todo{(All) discuss possible extension with self-connex}

	\medskip

% 2.2 - 
	\item \textit{Could you please better justify the choice of indicators (Internationalizationand Metropolization).}

	$\rightarrow$ \todo{(NZ) The choice of indicators has been better justified and explained based on citations of previous literature, already using these indicators to capture important globalisation processes in a city level network}

@@

	\item \textit{Link creation probability formula - industrial proximity: oversight to remove k (should not depend on k).}

	$\rightarrow$ \todo{(All) model description}

	\medskip

	\item \textit{"Model 4 also indicates the absence of overfitting": Can the authors be more precise?}
	% \todo{(JR) clarify}

	$\rightarrow$ This sentence was unclear, we meant that fit improvement in model 4 was not due to overfitting compared to other models. This was reformulated.

@@

	$\rightarrow$ \todo{(All) paper writing (ex jargon, clarity)}

	\medskip

%3.
	\item \textit{Clarfiy the methods and data. Explain what Amadeus is, how it is gathered etc. Explain the tools that are used to analyse it. Why those statistical packages and not others? It would also be useful to describe the data. How many cities and how many firms?}

	$\rightarrow$ \todo{(NZ) The ADAMDEUS dataset has been better explained in terms of sources and representativity}

@@

	\medskip

%4.
	\item \textit{And most importantly, clarify the theoretical framing. There is plenty of literature cited, but which of these provided inspiration for this study? For example, is this speaking to the 'global city networks' literature (e.g. Neal, Derudder) or more the economic connectivity literature (e.g. Acemoglu)?}

	$\rightarrow$ \todo{(All) Literature review/theoretical framing has been reviewed in order to justify the inspiration by the global city networks litterature}

@@

%It is with great interest that I read this paper, as I feel it has much to contribute to current debates on cities - in particular how to measure specific processes. The authors have done well to think about how the complexity of city processes might be measured, but I feel there are issues that need to be addressed before it is ready to be published in this journal.

\begin{enumerate}
%1)

	\item \textit{The main literature discussion appears to be in the introduction - but this is relatively high level. The research gap that the authors appear to be filling is the operationalisation of the processes (internationalisation, metropolisation, regionalisation and specialisation) within a city. However, it is unclear how this links to the processes you idetnfy as driving the network (listed 1-4 on pg.2) and then the model itself. The processes mentioned appear to be various ways of seeing proximity (ie agglomeration is spatial proximity, and previous linkages could be related to social or institutional proximity) - and whilst link back to previous work mentioned, there needs to be more discussion of past research.}

	$\rightarrow$ \todo{(NZ) The choice and the purpose of choosing thes indicators to identify economic processes has been better described in the introduction and hopefully it links better with the model}

@@

	\medskip

%2)
	\item \textit{The processes are mentioned in the methods section - but again exactly what is being measured and what each means is not well related to the process. For example, why exactly are geographic structures captured by internationalisation? Why have you chosen metropolisation to be represented in this way?}

	$\rightarrow$ \todo{(NZ) This has been better explained in the literature review and introduction}

@@

	\medskip

%3)
	\item \textit{More information on why the synthetic and real world models have been set up are needed. What do they bring to our understandings? You mention how internationalisation, metropolisation, fit within the model .... but what about regionalisation and specialisation? Are these latter just an outcome of the analysis, whilst the former are model parameters? Then why are they treated as the same in the introduction?}

	$\rightarrow$ \todo{(All) improve model description/contextualization}

@@

	\medskip

%4)
	\item \textit{Why in the statistical analysis do you then look at the 'most determining geo-economic factors influencing the creation of links between cities' - there was not real literature review to identify these - how do you then identify them? What is the relationship to the research question? Also pg 6 again describe the processes driving the networks (from pg 2 as noted above) - but these measures where not really discussed in when the model was being explained. How do they fit?}

	$\rightarrow$ \todo{(All) Literature on geo-economic factors has been enhanced - processes included}

@@

	\medskip

%5)
	\item \textit{The application of economic shocks appears to be an additional part of the model that is not properly discussed again in the literature review. I wonder if this is actually a different paper? I felt there were lots of interesting aspects to the research - and thinking about how to divide out the components to allow better discussion for each would benefit the research in that you could dive alot deeper into specific discussions.}

	$\rightarrow$ \todo{(All) justify proof of concept - add literature}
